---
title: "R Notebook"
output: html_notebook
---

## Autokláv riport


```{r, message=FALSE, warning=FALSE, include=FALSE}
library(stringr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(plotly)
library(xts)
library(dygraphs)
#library(knitr)
library(hms)
```

```{r, include=FALSE}
datafile <- "data/AU6801-NA1092AL00259.LOG"
#datafile <- "data/AU6801-NA1092AL00257.LOG"
autxt <- read_file(datafile)
s <- str_split(autxt, "\n")[[1]]   #sorokra tördeljük    #s[c(2:8, 16:19)]
inf <- str_subset(s, "^ ")
prt_par <- function(par){
  inf %>% str_subset(par) %>% str_split("[ ]{2,}") %>% .[[1]] %>% .[2]
}
```

Log fájl: `r datafile`  

Sterilizáló : `r prt_par("\\sSTERILIZALO")`  
PROGRAM KEZD.IDO : `r prt_par("\\sPROGRAM KEZD.IDO")`  
PROGRAM : `r prt_par("\\sPROGRAM")`  
Ciklus : `r inf[2]`  
TERMEK KOD : __`r prt_par("\\sTERMEK KOD")`__    
SARZSSZAM : `r prt_par("\\sSARZSSZAM")`  
ID.STERILIZALO : `r prt_par("\\sID.STERILIZALO")`  
MIN.STERIL.HOMERSEKLET : `r inf %>% str_subset("\\sMIN.STERIL.HOMERSEKLET") %>% str_split("[ ]{2,}") %>% .[[1]] %>% .[3]`  
MAX.STERIL.HOMERSEKLET : `r inf %>% str_subset("\\sMAX.STERIL.HOMERSEKLET") %>% str_split("[ ]{2,}") %>% .[[1]] %>% .[3]`  

```{r, include=FALSE}
f <-  str_split(autxt, "\\+\n")[[1]]
phase <- data.frame()
for( phaseIdx in 2:length(f) ){
  fl <- str_split(f[phaseIdx], "\n")[[1]]
  ph <- str_replace( str_replace( str_split(fl[1], "=")[[1]][2], "(^\\s)", ""), "[ ]+$", "")
  fld <- data.frame(fl)
  
  phase2 <- fld %>% 
    filter( (str_length(str_split(fl, " +", n = 2, simplify = TRUE)[,1]) == 1) & str_detect(fl, "#|\\$|\\+|@") ) %>%
    separate(fl, c("a", "t_", "p_", "te1", "te2", "te3", "te6"), "[ ]{1,}", extra = "drop", fill = "right") %>%
    separate(t_, c("m", "s"), ":" ) %>%
   
    transmute( t = make_datetime( hour = as.numeric(m) %/% 60, min = as.numeric(m) %% 60, sec = as.numeric(s) ), p = as.numeric(p_), TE1 = as.numeric(te1), TE2 = as.numeric(te2), TE3 = as.numeric(te3), TE6 = as.numeric(te6), ph = ph, idx = phaseIdx-1 )
  phase <- rbind(phase, phase2) 
}
phase$ido <- format(phase$t, "%H:%M:%S")
```

```{r}
phase  %>% select( ido, p, TE1, TE2, TE3, TE6, ph, idx)
```

```{r, echo=FALSE}
phLim <- phase %>% group_by(idx, ph) %>% summarise( start = min(t), end = max(t) ) %>% arrange(start)
table3<-xts(select(phase, -idx, -ph, -ido)[,-1],order.by=phase$t)
ribbonData <- as.factor(phase$idx )
dygraph(table3, main="Autokláv ciklus", ylab="hőmérséklet [°C]") %>% 
  dyRibbon(data = ribbonData, top = 1.0, bottom = 0.7, palette = c("#efefef", "#ffe6e6", "#ccebd6", "1F1FFF", "lightgreen", "azure", "khaki", "orange", "khaki", "lightblue", "khaki", "lightgreen", "khaki", "orange", "khaki")) %>%
  #dyRibbon(data = ribbonData, top = 1.0, bottom = 0.7, palette = terrain.colors(30) ) %>%
  dyEvent(phLim$start, phLim$ph, labelLoc = "bottom") %>%
  dyOptions(colors = RColorBrewer::brewer.pal(8, "Dark2")) %>%
  #dyRangeSelector() %>%
  dySeries("p", axis = 'y2') %>%
  dyAxis("y2", label = "nyomás [bar]") %>%
  dyAxis("x", label = "idő") %>%
  dyLegend(width = 600)
```

```{r, echo=FALSE}
phaseList <- phase %>% 
       group_by(idx, ph) %>% summarise( start = min(t), end = max(t), len = end-start ) %>%
       arrange(start) 
phaseList$startf <- format(phaseList$start, "%H:%M:%S")
phaseList$endf <- format(phaseList$end, "%H:%M:%S")
phaseList$lenf <- format(as_datetime( phaseList$len), "%H:%M:%S")
phaseList <- phaseList %>% select(idx, ph, startf, endf, lenf)
phaseList 
```